---
title: "Community Health"
execute:
  echo: false
format: 
  html:
    fig-width: 8
    fig-height: 4
    code-fold: false
---

The [*Organizational Maintenance*](./org.html) and [*Repository
Maintenance*](./repo.html) pages provide various insights into
maintenance deficits and needs across the whole organization and within
individual repositories. This page provides more detail on the various [CHAOSS
(*Community Health Analytics in Open Source Software*)
models](https://chaoss.community/kb-metrics-and-metrics-models/) used to
generate values shown on those two pages. Each of these conceptual models
aggregates various individual metrics, and aims to synthesise prominent aspects
of community health. This page provides insights into a range of those models,
assessed for each repository in the `epiverse-trace` and `reconhub` GitHub
organizations. Details of individual metrics can be seen on the [*Repository
Maintenance* page](./repo.html).

## Aggregate Community Health

This page shows aggregate community health scores for all repositories within
the `reconhub` and `epiverse-trace` organizations. Higher values describe
repositories with greater community health scores. Values for individual models
are standardised across all repositories to have mean values of zero and
standard deviations of one. These results are aggregated across thirteen
distinct models, leading to maximal aggregated values slightly exceeding that
value.

```{r load-pkg, echo = FALSE, message = FALSE}
library (orgmetrics)
```

```{r load-data}
dat_models <- readRDS (fs::path ("data", "results-models.Rds"))
```
```{r ojs-in-models}
ojs_define (models_in = dat_models)
```

```{ojs plot-latest}
Plot = import("https://esm.sh/@observablehq/plot")
```

```{ojs}
models_all = {
    return transpose(models_in).map(row => ({
        ...row,
    }));
}
models_final = models_all.filter(function(mod) {
    return mod.name === "final"
})
models_len = models_final.length
```


```{ojs plot-all-community-health-vars}
Plot.plot({
    height: 20 * models_len,
    marginLeft: 60,
    marginRight: 160,
    marginTop: 50,
    marginBottom: 50,
    axis: null,
    x: {
        axis: "top",
        grid: true,
        label: "Community Health"
    },
    y: { grid: true },
    marks: [
        Plot.barX(models_final, {
            y: "package",
            x: "value",
            sort: {y: "-x" },
            fill: "value",
        }),
        Plot.barX(models_final,
            Plot.pointer(
            {
                y: "package",
                x: "value",
                sort: {y: "-x" },
                stroke: "gray",
                fill: "value",
                strokeWidth: 2,
            })
        ),
        Plot.text(models_final, {
            x: (d) => d.value < 0 ? 0 : d.value,
            y: "package",
            text: "package",
            textAnchor: "start",
            fontSize: 16,
            dx: 5
        })
    ],
    color: {
        scheme: "Cool",
        type: "ordinal"
    }
})
```

## Individual models of community health

The following section shows values for each individual model of community
health for all repositories.

```{ojs load-json-data}
// -------- READ JS DATA
json_data = FileAttachment("results-json-data.json").json();
rm_metrics_models = json_data['rm_metrics_models'];
rm_models = rm_metrics_models['models'];
rm_model_text = rm_metrics_models['model_names'];
modelsTextMap = rm_model_text.reduce((map, item) => {
    return map.set(String(item.name), item.airtable_name);
}, new Map());
modelsUrlMap = rm_model_text.reduce((map, item) => {
    return map.set(String(item.name), item.url);
}, new Map());
```


```{ojs comm-health-vars}
commHealthVars = Array.from(modelsTextMap.keys());
commHealthText = commHealthVars.map(item => {
    return modelsTextMap.has(item) ? modelsTextMap.get(item) : "";
})
viewof commHealthVar = Inputs.select(
    rm_model_text,
    {
        multiple: "false",
        label: "Community Health Variable",
        format: x => x.airtable_name,
    }
);

htl.html`<div>
Click this link for description of the <a href="${commHealthVar.url}" target="_blank">
<i>${commHealthVar.airtable_name}</i></a> CHAOSS model.
</div>`
```

```{ojs}
models_filtered = models_all.filter(function(mod) {
    return mod.name === commHealthVar.name
})
```


```{ojs plot-filtered-community-health-var}
Plot.plot({
    height: 20 * models_len,
    marginLeft: 60,
    marginRight: 160,
    marginTop: 50,
    marginBottom: 50,
    axis: null,
    x: {
        axis: "top",
        grid: true,
        label: "Community Health"
    },
    y: { grid: true },
    marks: [
        Plot.barX(models_filtered, {
            y: "package",
            x: "value",
            sort: {y: "-x" },
            fill: "value",
        }),
        Plot.barX(models_filtered,
            Plot.pointer(
            {
                y: "package",
                x: "value",
                sort: {y: "-x" },
                stroke: "gray",
                fill: "value",
                strokeWidth: 2,
            })
        ),
        Plot.text(models_filtered, {
            x: (d) => d.value < 0 ? 0 : d.value,
            y: "package",
            text: "package",
            textAnchor: "start",
            fontSize: 16,
            dx: 5
        })
    ],
    color: {
        scheme: "Cool",
        type: "ordinal"
    }
})
```

## Community health for individual repositories

The following section shows all models of community health for a selected
repository. The names of the models are hyperlinked to the definitions within
the specific pages of the [CHAOSS
models](https://chaoss.community/kbtopic/all-metrics-models/).

```{ojs get-all-models}
// Get array of unique repo names for input selector:
reposAll = models_all.map(function(item) {
    return item.package;
});
repos = Array.from(new Set(reposAll));
repoSet = localStorage.getItem("orgmetricsRepo") || repos [0]
viewof repo = Inputs.select(
    repos,
    {
        multiple: false,
        value: repoSet,
        label: htl.html`<b>Repository:</b>`
    }
)
tmpval = localStorage.setItem("orgmetricsRepo", repo.toString());
```

```{ojs}
models_with_url = models_all.map(item => {
    const key = item.name;
    const url = modelsUrlMap.has(key) ? modelsUrlMap.get(key) :
        "https://chaoss.community/kbtopic/all-metrics-models/";
    const fullname = modelsTextMap.has(key) ? modelsTextMap.get(key) : item.name
    return {
        ...item,
        fullname: fullname,
        url: url
    }
})
model_repo = models_with_url.filter(function(mod) {
    return mod.package === repo && mod.name !== "final"
})
model_repo_len = model_repo.length
bar_ht_mult = model_repo_len > 20 ? 20 : 40;
```



```{ojs plot-filtered-repo}
Plot.plot({
    height: bar_ht_mult * model_repo_len,
    marginLeft: 60,
    marginRight: 160,
    marginTop: 50,
    marginBottom: 50,
    axis: null,
    x: {
        axis: "top",
        grid: true,
        label: "Community Health"
    },
    y: { grid: true },
    marks: [
        Plot.barX(model_repo, {
            y: d => d.fullname,
            x: d => d.value,
            sort: {y: "-x" },
            fill: d => d.value,
        }),
        Plot.barX(model_repo,
            Plot.pointer(
            {
                y: d => d.fullname,
                x: d => d.value,
                sort: {y: "-x" },
                stroke: "gray",
                fill: d => d.value,
                strokeWidth: 2,
            })
        ),
        Plot.text(model_repo, {
            x: d => d.value,
            y: d => d.fullname,
            text: d => d.fullname,
            href: d => d.url,
            textAnchor: "start",
            fontSize: 16,
            dx: 5
        })
    ],
    color: {
        scheme: "Cool",
        type: "ordinal"
    }
})
```
